Constructive Preference Elicitation by Setwise Max-margin Learning

### 2016-04-16 paper/ijcai16.tex
paper: one point is bogus IMO.

The goal of our setwise max-margin approach is twofold. First, for any
given set size $k\geq 1$, we want to find a {\em set} of $k$ weight
vectors $\vw^{1}, \ldots, \vw^{k}$, chosen so that all user-provided
preferences are satisfied by the largest possible margin (%
%i.e. all
%weight vectors are consistent with respect to the user responses
%$\calD$, 
modulo inconsistencies) and so that they are maximally
diverse.  Second, we want to construct a {\em set} of $k$
configurations $\vx^{1}, \ldots, \vx^{k}$, so that each configuration
$\vx^{i}$ is the ``best'' possible option when evaluated according to
the corresponding $\vw^{i}$ and configurations are maximally diverse
among each other. These options will be later used to formulate
queries.

@@

The second goal requires \stefano{reviewer 2, rephrase: to jointly maximize the utility of each
$\vx^{i}$ according to its corresponding weight vector $\vw^i$ and its
scoring difference with respect to the other configurations $\vx^j$ in
the set. We achieve this by maximizing the sum of utilities
$\sum_{i=1}^k \langle \vw^{i}, \vx^{i} \rangle$ and} adding ranking
constraints of the form
$\langle \vw^{i}, \vx^{i} - \vx^{j} \rangle \geq \mu$ for all
$i,j\in[k]$, $i \ne j$.

>>>>

The goal of our setwise max-margin approach is twofold. First, for any
given set size $k\geq 1$, we want to find a {\em set} of $k$ weight
vectors $\vw^{1}, \ldots, \vw^{k}$, chosen so that all user-provided
preferences are satisfied by the largest possible margin (%
%i.e. all
%weight vectors are consistent with respect to the user responses
%$\calD$, 
modulo inconsistencies) and so that they are maximally
diverse.  Second, we want to construct a {\em set} of $k$
configurations $\vx^{1}, \ldots, \vx^{k}$, so that each configuration
$\vx^{i}$ is the ``best'' possible option when evaluated according to
the corresponding $\vw^{i}$ {\em and} configurations are maximally diverse
among each other. These options will be later used to formulate
queries.

@@

The second goal requires \stefano{I think this is correct as-is: the second
reviewer thinks that the second goal is to maximize diversity; above we clearly
state that it requires to find diverse {\em and} good configurations} to jointly maximize the utility of each
$\vx^{i}$ according to its corresponding weight vector $\vw^i$ and its
scoring difference with respect to the other configurations $\vx^j$ in
the set. We achieve this by maximizing the sum of utilities
$\sum_{i=1}^k \langle \vw^{i}, \vx^{i} \rangle$ and adding ranking
constraints of the form
$\langle \vw^{i}, \vx^{i} - \vx^{j} \rangle \geq \mu$ for all
$i,j\in[k]$, $i \ne j$.
